Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-15 appendix.qmd
Updated the arrangement

\newpage

@@

```{r}
#| label: fig-assign-data
#| fig-cap: "Binning the data. Points are assigned to the nearest centroid. If a point is equidistant from multiple centroids, assigned to the lowest centroid."
#| fig-width: 9
#| fig-height: 6

@@

```{r}
#| label: fig-tri-param
#| fig-cap: "The components of the right triangle illustrating notation."
#| out-width: 30%

@@

@@

# Combine the plots using the layout
(error_umap_plot_pbmc + nldr1c + nldr2c) +
  plot_layout(design = layout_design)
```
The layout a (@fig-pbmc-mse-umap) is generated from the hyper-parameters suggested by @chen2024, and the layout b (@fig-pbmc-mse-umap) is with suggested hyper-parameters by scDEED to be more accurate. The layout a and b contain $46$ and $83$ dubious cells respectively.

>>>>

@@

```{r}
#| label: fig-assign-data
#| fig-cap: "Binning the data. Points are assigned to the nearest centroid. If a point is equidistant from multiple centroids, assigned to the lowest centroid."
#| fig-width: 9
#| fig-height: 6
#| fig-pos: H

@@

```{r}
#| label: fig-tri-param
#| fig-cap: "The components of the right triangle illustrating notation."
#| out-width: 30%
#| fig-pos: H

@@

The layout a (@fig-pbmc-mse-umap) is generated from the hyper-parameters suggested by @chen2024, and the layout b (@fig-pbmc-mse-umap) is with suggested hyper-parameters by scDEED to be more accurate. The layout a and b contain $46$ and $83$ dubious cells respectively.

@@

# Combine the plots using the layout
(error_umap_plot_pbmc + nldr1c + nldr2c) +
  plot_layout(design = layout_design)
```
